Identifying Heterogeneity in SAR Data with New Test Statistics

### 2024-11-24 Text/2024PresentationsChina.tex
Happy with the slides

%\usefonttheme{professionalfonts}
\usepackage[T1]{fontenc}
\renewcommand*\familydefault{\sfdefault}

\usepackage{beamerthemesplit}
\usepackage{graphicx}
\graphicspath{{./Figures/}}

\usepackage{bm,bbm,bbding}
\usepackage{natbib}
\usepackage{siunitx}
\usepackage{texnames}
\usepackage{algorithm,algpseudocode}
\usepackage{multirow}
\usepackage{booktabs}
\usepackage{amsmath}
\usepackage{mathabx}
\usepackage{scalerel,stackengine}
\stackMath
\newcommand\reallywidehat[1]{%
	\savestack{\tmpbox}{\stretchto{%
			\scaleto{%
				\scalerel*[\widthof{\ensuremath{#1}}]{\kern-.6pt\bigwedge\kern-.6pt}%
				{\rule[-\textheight/2]{1ex}{\textheight}}%WIDTH-LIMITED BIG WEDGE
			}{\textheight}% 
		}{0.5ex}}%
	\stackon[1pt]{#1}{\tmpbox}%
}
\parskip 1ex

@@

Although we know that $\bar{\bm X}$ and $\widehat{\text{CV}}(\overline X) $ are independent \citep{OnaCharacterizationoftheGammaDistributiontheIndependenceoftheSampleMeanandtheSampleCoefficientofVariation}, we don't know the distribution of~\eqref{eq:CV}.
\end{frame}

@@

It is robust, we don't know its distribution under the $\Gamma_{\text{SAR}}$ model.
\end{frame}

@@

Now, given the random sample $\bm Z=(Z_1,Z_2,\dots,Z_n)$ and its sorted version $Z_{(1)},Z_{(2)},\dots,Z_{(n)}$, we can 
\begin{itemize}
	\item estimate $F^{-1}$ by the empirical cumulative distribution function,
	\item approximate the derivative with finite differences (called ``spacings''),
	\item approximate the integral with a summation.
\end{itemize}

@@

{\setbeamercolor{background canvas}{bg=anti-flashwhite}
\begin{frame}{Application to simulated data: $S_{\widehat{\text{CV}}}$, $S_{\widehat{\text{CV}_{\text{MnAD}}}}$, and $S_{\widetilde{H}_{\text{AO}}}$ $p$-values}
\centering
{\includegraphics[width=.32\linewidth]{../Figures/PNG/cv_pvalues_Phantom_4_z1} }
{\includegraphics[width=.32\linewidth]{../Figures/PNG/mnad_p_values_Phantom_mnad_7_z1} }
{\includegraphics[width=.32\linewidth]{../Figures/PNG/H_pvalue_Phantom_4_z1_200b} }
\end{frame}
}

{\setbeamercolor{background canvas}{bg=anti-flashwhite}
\begin{frame}{Application to Sentinel~2 data}
\centering
\includegraphics[width=.335\linewidth]{../Figures/PNG/Sentinel2_Illinois_lake}
\includegraphics[width=.32\linewidth]{../Figures/PNG/lake_512}
\includegraphics[width=.32\linewidth]{../Figures/PNG/H_pvalue_lake_512_36L_AO_100b}
\end{frame}
}

>>>>

\usepackage[T1]{fontenc}
\usefonttheme{serif}

%\usepackage{beamerthemesplit}
\usepackage{graphicx}
\graphicspath{{./Figures/PNG/}}

\usepackage{bm,bbm,bbding}
\usepackage{natbib}
\usepackage{siunitx}
\usepackage{texnames}
\usepackage{multirow}
\usepackage{booktabs}
\usepackage{amsmath}
\usepackage{mathabx}
\usepackage{scalerel,stackengine}
\stackMath
\newcommand\reallywidehat[1]{%
	\savestack{\tmpbox}{\stretchto{%
			\scaleto{%
				\scalerel*[\widthof{\ensuremath{#1}}]{\kern-.6pt\bigwedge\kern-.6pt}%
				{\rule[-\textheight/2]{1ex}{\textheight}}%WIDTH-LIMITED BIG WEDGE
			}{\textheight}% 
		}{0.5ex}}%
	\stackon[1pt]{#1}{\tmpbox}%
}
\parskip 1ex

@@

Although we know that $\overline{\bm X}$ and $\widehat{\text{CV}}(\overline X) $ are independent \citep{OnaCharacterizationoftheGammaDistributiontheIndependenceoftheSampleMeanandtheSampleCoefficientofVariation}, we don't know the distribution of~\eqref{eq:CV}.
\end{frame}

@@

It is robust, but we don't know its distribution under the $\Gamma_{\text{SAR}}$ model.
\end{frame}

@@

Now, given the random sample $\bm Z=(Z_1,Z_2,\dots,Z_n)$ and its sorted version $Z_{(1)},Z_{(2)},\dots,Z_{(n)}$, we can 
\begin{itemize}
	\item estimate $F$ by the empirical cumulative distribution function,
	\item approximate the derivative with finite differences (called ``spacings''),
	\item approximate the integral with a summation.
\end{itemize}

@@

{\setbeamercolor{background canvas}{bg=anti-flashwhite}
\begin{frame}{Application to simulated data: $S_{\widehat{\text{CV}}}$, $S_{\widehat{\text{CV}_{\text{MnAD}}}}$, and $S_{\widetilde{H}_{\text{AO}}}$ $p$-values}
\centering
{\includegraphics[width=.33\linewidth]{../Figures/PNG/cv_pvalues_Phantom_4_z1} }
{\includegraphics[width=.33\linewidth]{../Figures/PNG/mnad_p_values_Phantom_mnad_7_z1} }
{\includegraphics[width=.33\linewidth]{../Figures/PNG/H_pvalue_Phantom_4_z1_200b} }
\end{frame}
}

{\setbeamercolor{background canvas}{bg=anti-flashwhite}
	\begin{frame}{Rotterdam: optical and Sentinel~2 data}
		\centering
\includegraphics[width=.48\linewidth]{../Figures/PNG/Rotterdam} 
\includegraphics[width=.48\linewidth]{../Figures/PNG/Rotterdam_1024}
	\end{frame}
}

{\setbeamercolor{background canvas}{bg=anti-flashwhite}
	\begin{frame}{Rotterdam: $S_{\widehat{\text{CV}}}$, $S_{\widehat{\text{CV}_{\text{MnAD}}}}$, and $S_{\widetilde{H}_{\text{AO}}}$ $p$-values}
		\centering
\visible<1->{\includegraphics[width=.32\linewidth]{../Figures/PNG/cv_Rotterdam}}
\visible<2->{\includegraphics[width=.32\linewidth]{../Figures/PNG/mnad_Rotterdam}}
\visible<3->{\includegraphics[width=.32\linewidth]{../Figures/PNG/Entropy_AO_Rotterdam_1024}}
	\end{frame}
}

{\setbeamercolor{background canvas}{bg=anti-flashwhite}
\begin{frame}{Illinois: optical, Sentinel~2, and $p$-values}
\centering
\includegraphics[width=.335\linewidth]{../Figures/PNG/Sentinel2_Illinois_lake}
\includegraphics[width=.32\linewidth]{../Figures/PNG/lake_512}
\includegraphics[width=.32\linewidth]{../Figures/PNG/H_pvalue_lake_512_36L_AO_100b}
\end{frame}
}
